### 2016-02-08 Manuscript/BiologyLetters/Table_results.tex
Updated results in text (no threshold)
added colour and black and white table figures

% latex table generated in R 3.2.0 by xtable 1.7-4 package
% Sat Jun 20 17:19:07 2015

@@

\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels (without any character threshold; results from the 286 matrices). The coverage represents the proportion of taxa with available morphological data. The left vertical bar represents 25\% of available data (``low'' coverage if \textless 25\%); The right vertical bar represents 75\% of available data (``high'' coverage if \textgreater 75\%). When the Net Relatedness Index (NRI) and the Nearest Taxon Index (NTI) are negative, taxa are more phylogenetically dispersed than expected by chance; when NRI or NTI are positive, taxa are more phylogenetically clustered by expected by chance. Significant NRI or NTI are highlighted in bold. *p \textless 0.05; **p \textless 0.01; ***p \textless 0.001.} \\ 

@@

  Afrosoricida & species & 23/42 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & 1.75 & 1.08 \\ 
  Carnivora & family & 14/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.63 & 0.6 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{54/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.81**} & \textbf{1.78*} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{76/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{7.66**} & \textbf{0.85} \\ 

@@

  Cetartiodactyla & genus & 100/128 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & 0.85 & 0.94 \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{171/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{1.92*} & \textbf{-0.46} \\ 
  Chiroptera & family & 15/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & -0.28 & 0.56 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{93/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{13.47**} & \textbf{1.1} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{215/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{8.82**} & \textbf{1.22} \\ 

@@

  Cingulata & genus & 8/9 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar14.pdf} & 1.51 & -1.57 \\ 
  \textbf{Cingulata} & \textbf{species} & \textbf{9/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar15.pdf} & \textbf{1.9*} & \textbf{0.11} \\ 

@@

  Dasyuromorphia & genus & 8/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar17.pdf} & -0.75 & -1.07 \\ 
  Dasyuromorphia & species & 9/64 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar18.pdf} & -0.88 & -0.34 \\ 

@@

  Didelphimorphia & species & 42/84 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar24.pdf} & -1.65 & 0.2 \\ 

@@

  Diprotodontia & genus & 25/38 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar26.pdf} & -1.13 & -1.31 \\ 
  Diprotodontia & species & 31/126 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar27.pdf} & 0.48 & -1.77 \\ 

@@

  Erinaceomorpha & species & 21/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar30.pdf} & -1.07 & -0.2 \\ 

@@

  Lagomorpha & genus & 5/12 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar35.pdf} & -1.06 & -0.95 \\ 
  Lagomorpha & species & 12/86 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar36.pdf} & -0.62 & -1.88 \\ 

@@

  Macroscelidea & species & 12/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar39.pdf} & -1.3 & -1.06 \\ 
  Microbiotheria & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar40.pdf} &   &   \\ 
  Microbiotheria & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar41.pdf} &   &   \\ 
  Microbiotheria & species & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar42.pdf} &   &   \\ 
  Monotremata & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar43.pdf} &   &   \\ 
  Monotremata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar44.pdf} & -0.72 & -0.69 \\ 
  Monotremata & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar45.pdf} & -0.97 & -0.97 \\ 
  Notoryctemorphia & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar46.pdf} &   &   \\ 
  Notoryctemorphia & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar47.pdf} &   &   \\ 
  Notoryctemorphia & species & 0/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar48.pdf} &   &   \\ 
  Paucituberculata & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar49.pdf} &   &   \\ 
  Paucituberculata & genus & 3/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar50.pdf} &   &   \\ 
  Paucituberculata & species & 5/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar51.pdf} &   &   \\ 
  Peramelemorphia & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar52.pdf} &   &   \\ 
  Peramelemorphia & genus & 7/7 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar53.pdf} &   &   \\ 
  Peramelemorphia & species & 16/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar54.pdf} & -0.13 & 0.97 \\ 
  Perissodactyla & family & 3/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar55.pdf} &   &   \\ 
  Perissodactyla & genus & 6/6 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar56.pdf} &   &   \\ 
  Perissodactyla & species & 10/16 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar57.pdf} & -0.07 & -2.63 \\ 
  Pholidota & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar58.pdf} &   &   \\ 
  Pholidota & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar59.pdf} &   &   \\ 
  Pholidota & species & 4/8 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & 1.18 & 0.94 \\ 
  Pilosa & family & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} & 1.87 & 2 \\ 
  Pilosa & genus & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} & -0.96 & 0.36 \\ 
  \textbf{Pilosa} & \textbf{species} & \textbf{5/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & \textbf{1.28} & \textbf{2.38*} \\ 
  Primates & family & 15/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar64.pdf} &   &   \\ 
  Primates & genus & 48/68 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar65.pdf} & -0.35 & -1.33 \\ 
  Primates & species & 64/351 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar66.pdf} & -0.67 & -1.27 \\ 
  Proboscidea & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar67.pdf} &   &   \\ 
  Proboscidea & genus & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar68.pdf} &   &   \\ 
  Proboscidea & species & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar69.pdf} & -0.69 & -0.69 \\ 
  Rodentia & family & 18/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} & 0.66 & -0.98 \\ 
  Rodentia & genus & 82/450 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} & -1.66 & 1.55 \\ 
  \textbf{Rodentia} & \textbf{species} & \textbf{90/2094} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & \textbf{2.76*} & \textbf{2.34*} \\ 
  Scandentia & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar73.pdf} &   &   \\ 
  Scandentia & genus & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar74.pdf} & -0.74 & -0.74 \\ 
  Scandentia & species & 3/20 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar75.pdf} & -1.88 & -0.84 \\ 
  Sirenia & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar76.pdf} &   &   \\ 
  Sirenia & genus & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar77.pdf} &   &   \\ 
  Sirenia & species & 4/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar78.pdf} &   &   \\ 
  Soricomorpha & family & 3/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar79.pdf} & -0.98 & -0.99 \\ 
  \textbf{Soricomorpha} & \textbf{genus} & \textbf{19/43} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar80.pdf} & \textbf{7.11**} & \textbf{2.59**} \\ 
  \textbf{Soricomorpha} & \textbf{species} & \textbf{21/392} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar81.pdf} & \textbf{10.65**} & \textbf{3.56**} \\ 
  Tubulidentata & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar82.pdf} &   &   \\ 
  Tubulidentata & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar83.pdf} &   &   \\ 
  Tubulidentata & species & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar84.pdf} &   &   \\ 

>>>>

% latex table generated in R 3.2.3 by xtable 1.8-0 package
% Mon Feb  8 22:09:15 2016

@@

\caption{Number of taxa with available cladistic data for mammalian orders at three taxonomic levels. The coverage represents the proportion of taxa with available morphological data. The left vertical bar represents 25\% of available data (``low'' coverage if \textless 25\%); The right vertical bar represents 75\% of available data (``high'' coverage if \textgreater 75\%). When the Net Relatedness Index (NRI) and the Nearest Taxon Index (NTI) are negative, taxa are more phylogenetically dispersed than expected by chance; when NRI or NTI are positive, taxa are more phylogenetically clustered by expected by chance. Significant NRI or NTI are highlighted in bold. One star (*) represents a p-value between 0.05 and 0.005; two starts between 0.005 and 0.0005 and three stars a p-value less than 0.0005.} \\ 

@@

  Afrosoricida & species & 23/42 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar3.pdf} & 1.52 & 1.1 \\ 
  Carnivora & family & 14/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar4.pdf} & 0.65 & 0.55 \\ 
  \textbf{Carnivora} & \textbf{genus} & \textbf{52/125} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar5.pdf} & \textbf{4.27**} & \textbf{1.26} \\ 
  \textbf{Carnivora} & \textbf{species} & \textbf{75/283} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar6.pdf} & \textbf{7.24**} & \textbf{0.8} \\ 

@@

  Cetartiodactyla & genus & 97/128 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar8.pdf} & 0.7 & 1.28 \\ 
  \textbf{Cetartiodactyla} & \textbf{species} & \textbf{169/310} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar9.pdf} & \textbf{1.82*} & \textbf{-0.24} \\ 
  Chiroptera & family & 15/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar10.pdf} & -0.23 & 0.61 \\ 
  \textbf{Chiroptera} & \textbf{genus} & \textbf{92/202} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar11.pdf} & \textbf{13.07**} & \textbf{0.99} \\ 
  \textbf{Chiroptera} & \textbf{species} & \textbf{214/1053} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar12.pdf} & \textbf{9.21**} & \textbf{1.27} \\ 

@@

  Cingulata & genus & 8/9 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar14.pdf} & 1.48 & -1.54 \\ 
  \textbf{Cingulata} & \textbf{species} & \textbf{9/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar15.pdf} & \textbf{2.06*} & \textbf{0.2} \\ 

@@

  Dasyuromorphia & genus & 8/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar17.pdf} & -0.78 & -1.06 \\ 
  Dasyuromorphia & species & 9/64 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar18.pdf} & -0.86 & -0.37 \\ 

@@

  Didelphimorphia & species & 42/84 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar24.pdf} & -1.61 & 0.12 \\ 

@@

  Diprotodontia & genus & 25/38 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar26.pdf} & -1.15 & -1.33 \\ 
  Diprotodontia & species & 31/126 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar27.pdf} & 0.44 & -1.79 \\ 

@@

  Erinaceomorpha & species & 21/22 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar30.pdf} & -1.04 & -0.25 \\ 

@@

  Lagomorpha & genus & 5/12 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar35.pdf} & -0.95 & -0.94 \\ 
  Lagomorpha & species & 12/86 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar36.pdf} & -0.62 & -1.96 \\ 

@@

  Macroscelidea & species & 12/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar39.pdf} & -1.24 & -1.2 \\ 
  Mammalia (class) & family & 129/148 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar40.pdf} & -1.19 & 1.09 \\ 
  \textbf{Mammalia (class)} & \textbf{genus} & \textbf{517/1186} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar41.pdf} & \textbf{-5.19} & \textbf{3.71**} \\ 
  \textbf{Mammalia (class)} & \textbf{species} & \textbf{847/5017} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar42.pdf} & \textbf{-7.75} & \textbf{3.54**} \\ 
  Microbiotheria & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar43.pdf} &   &   \\ 
  Microbiotheria & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar44.pdf} &   &   \\ 
  Microbiotheria & species & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar45.pdf} &   &   \\ 
  Monotremata & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar46.pdf} &   &   \\ 
  Monotremata & genus & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar47.pdf} & -0.68 & -0.69 \\ 
  Monotremata & species & 2/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar48.pdf} & -1.01 & -1 \\ 
  Notoryctemorphia & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar49.pdf} &   &   \\ 
  Notoryctemorphia & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar50.pdf} &   &   \\ 
  Notoryctemorphia & species & 0/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar51.pdf} &   &   \\ 
  Paucituberculata & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar52.pdf} &   &   \\ 
  Paucituberculata & genus & 3/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar53.pdf} &   &   \\ 
  Paucituberculata & species & 5/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar54.pdf} &   &   \\ 
  Peramelemorphia & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar55.pdf} &   &   \\ 
  Peramelemorphia & genus & 7/7 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar56.pdf} &   &   \\ 
  Peramelemorphia & species & 16/18 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar57.pdf} & -0.14 & 0.91 \\ 
  Perissodactyla & family & 3/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar58.pdf} &   &   \\ 
  Perissodactyla & genus & 6/6 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar59.pdf} &   &   \\ 
  Perissodactyla & species & 10/16 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar60.pdf} & -0.1 & -2.77 \\ 
  Pholidota & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar61.pdf} &   &   \\ 
  Pholidota & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar62.pdf} &   &   \\ 
  Pholidota & species & 4/8 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar63.pdf} & 1.14 & 0.97 \\ 
  Pilosa & family & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar64.pdf} & 2.01 & 1.96 \\ 
  Pilosa & genus & 4/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar65.pdf} & -0.91 & 0.36 \\ 
  \textbf{Pilosa} & \textbf{species} & \textbf{5/29} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar66.pdf} & \textbf{1.18} & \textbf{2.35**} \\ 
  Primates & family & 15/15 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar67.pdf} &   &   \\ 
  Primates & genus & 48/68 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar68.pdf} & -0.37 & -1.39 \\ 
  Primates & species & 64/351 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar69.pdf} & -0.66 & -1.4 \\ 
  Proboscidea & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar70.pdf} &   &   \\ 
  Proboscidea & genus & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar71.pdf} &   &   \\ 
  Proboscidea & species & 2/3 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar72.pdf} & -0.67 & -0.72 \\ 
  Rodentia & family & 18/32 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar73.pdf} & 0.66 & -0.95 \\ 
  \textbf{Rodentia} & \textbf{genus} & \textbf{82/450} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar74.pdf} & \textbf{-1.81} & \textbf{1.7*} \\ 
  \textbf{Rodentia} & \textbf{species} & \textbf{90/2094} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar75.pdf} & \textbf{2.66**} & \textbf{2.36**} \\ 
  Scandentia & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar76.pdf} &   &   \\ 
  Scandentia & genus & 2/5 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar77.pdf} & -0.77 & -0.76 \\ 
  Scandentia & species & 3/20 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar78.pdf} & -2 & -0.8 \\ 
  Sirenia & family & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar79.pdf} &   &   \\ 
  Sirenia & genus & 2/2 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar80.pdf} &   &   \\ 
  Sirenia & species & 4/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar81.pdf} &   &   \\ 
  Soricomorpha & family & 3/4 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar82.pdf} & -0.98 & -0.97 \\ 
  \textbf{Soricomorpha} & \textbf{genus} & \textbf{19/43} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar83.pdf} & \textbf{7.07**} & \textbf{2.64**} \\ 
  \textbf{Soricomorpha} & \textbf{species} & \textbf{21/392} & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar84.pdf} & \textbf{10.17**} & \textbf{3.36**} \\ 
  Tubulidentata & family & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar85.pdf} &   &   \\ 
  Tubulidentata & genus & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar86.pdf} &   &   \\ 
  Tubulidentata & species & 1/1 & \includegraphics[width=0.20\linewidth, height=0.05\linewidth]{Table_figures/bar87.pdf} &   &   \\ 
